---
title: "ESM 206 Lab 8"
author: "Michelle Geldin"
date: "11/15/2021"
output: html_document
---

```{r setup, include=FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(corrplot)
library(stargazer)
library(broom)
library(modelsummary)
library(here)
```


## Read in data

```{r}
homes <- read_csv(here("slo_homes.csv"))
```

A little bit of cleaning:

Make a subset called homes_sub that only contains observations (rows) where the city is:

- San Luis Obispo
- Arroyo Grande
- Atascadero
- Santa Maria-Orcutt

```{r}
homes_sub <- homes %>%
  filter(City %in% c("San Luis Obispo", "Arroyo Grande", "Atascadero", "Santa Maria-Orcutt")) # This will look for each item in sequential order if you don't use %in% so use %in%!
  
```

## Do a little exploring of our data

Summary statistics (home price, based on city and sale status)

- Find and return in a nice summary table the mean and standard deviation of home price. grouped by city and sale status.
```{r, include = FALSE, eval = FALSE}
homes_sub %>%
  group_by(City, Status) %>%
  summarize(mean_price = mean(Price, na.rm = TRUE),
            sd_price = sd(Price, na.rm = TRUE))

# If I don't even want to run this code, add eval equals false in the top code. This will skip over to the next piece.

ggplot(data = homes_sub, aes(x = Price)) +
  geom_density(aes(color = City, fill = City), alpha = 0.3) + #alpha has to do with the level of opaqueness of the fill colors.
  scale_x_continuous(limits = c(0, 3e6))#o.3 is not assigned to a variable, it's assigned to a constant so we put it outside the parentheses? # Scale x continuous can change variable on the x axis only if it's a continuous variable. If it wasn't you can use scale x discrete or something. 
                     
```
Explore the relationship (visual data exploration) between square footage and home price. Change the point COLOR by City, and the point shape by sale status.

```{r}
ggplot(data = homes_sub, aes(x = SqFt, y = Price)) +
  geom_point() +
  geom_smooth(method = "lm")
  
```
## Model the relationship with home price as the Dependant Variable (or outcome variable or DV)

```{r}
homes_lm_1 <- lm(Price ~City + Bedrooms + Bathrooms + SqFt + PricePerSqFt + Status, data = homes_sub) #Price is dependent variable here

# Make a subset that only contains the quantitative variables
homes_quant <- homes_sub %>%
  select(Price:PricePerSqFt)

homes_cor <- cor(homes_quant)
homes_cor

corrplot(homes_cor, method = "square")

# How would I explore diagnostic plots?
plot(homes_lm_1)
```


Try another model (homes_lm_2) where we simplify this a bit

- City
- SqFt
- Status

```{r}
homes_lm_2 <- lm(Price ~ City + SqFt + Status, data = homes_sub)
homes_lm_2

plot(homes_lm_2)
```
Find the AIC value of each model:

```{r}
AIC(homes_lm_1)
AIC(homes_lm_2)
```
Lower AIC values indicate a better balance between model fit and complexity. Maybe neither are the models were looking for. Maybe we need a better intermediate model.

Try another permutation of this model that you think might make sense. Check out and compare the model fit, outputs, and AIC value.

```{r}
homes_lm_3 <- lm(Price ~ City + SqFt + Status + Bedrooms, data = homes_sub)

summary(homes_lm_3)
AIC(homes_lm_3)
  
```
Use `modelsummary` to show model outputs side-by-side:

```{r}
modelsummary(list(homes_lm_1, homes_lm_2, homes_lm_3))
```

## Start making predictions with this model

Use `broom::augment()`

```{r}
homes_predicted <- augment(homes_lm_1)
```

Use the `predict()` function to try out your model on new scenarios that you create.